% !TEX program = pdflatex-dev
% !TEX options = --shell-escape --synctex=1 --interaction=nonstopmode %DOCFILE%

% \iffalse meta-comment
%
% Copyright 2021-2022
% The LaTeX Project and any individual authors listed elsewhere
% in this file.
%
% This file is part of the LaTeX base system.
% -——————————————
%
% It may be distributed and/or modified under the
% conditions of the LaTeX Project Public License, either version 1.3c
% of this license or (at your option) any later version.
% The latest version of this license is in
%    https://www.latex-project.org/lppl.txt
% and version 1.3c or later is part of all distributions of LaTeX
% version 2008 or later.
%
% This file has the LPPL maintenance status "maintained".
%
% The list of all files belonging to the LaTeX base distribution is
% given in the file `manifest.txt'. See also `legal.txt' for additional
% information.
%
% The list of derived (unpacked) files belonging to the distribution
% and covered by LPPL is defined by the unpacking scripts (with
% extension .ins) which are part of the distribution.
%
% \fi
% Filename: ltnews35.tex
%
% This is issue 35 of LaTeX News.
\DocumentMetadata{pdfversion=1.7}
\NeedsTeXFormat{LaTeX2e}[2020-02-02]

\documentclass{ltnews}


%%  Maybe needed only for Chris' inadequate system:
\providecommand\Dash {\unskip \textemdash}

%% NOTE:  Chris' preferred hyphens!
%%\showhyphens{parameters}
%%  \hyphenation{because parameters parameter}
\usepackage[scheme=plain]{ctex}

\newif\ifenglish
\newif\ifnoheadfoot
\englishtrue
\noheadfootfalse

\usepackage{verbatim}

\ifenglish
  \def\english{\color[gray]{0.5}}
  \def\endenglish{\medskip}
\else 
  \let\english\comment
  \let\endenglish\endcomment
\fi 
\def\TODO{\textcolor{red}{TODO: }}
\raggedbottom

\makeatletter
\ifnoheadfoot 
  \def\@oddfoot{}
  \def\@evenfoot{}
  \def\@oddhead{}
  \def\@evenfoot{}
  \renewcommand{\ps@titlepage}{%
   \renewcommand{\@oddfoot}{\hfill}%
   \renewcommand{\@evenfoot}{\hfill}%
   \renewcommand{\@oddhead}{\@indiciafont\@indicia\hfill}%
   \renewcommand{\@evenhead}{\@indiciafont\@indicia\hfill}%
}
\fi 
\makeatother

\usepackage{lmodern,url,hologo}

\usepackage{csquotes}
\usepackage{multicol}
\usepackage{color}

\providecommand\hook[1]{\texttt{#1}}

\providecommand\meta[1]{$\langle$\textrm{\itshape#1}$\rangle$}
\providecommand\option[1]{\texttt{#1}}
\providecommand\env[1]{\texttt{#1}}
\providecommand\Arg[1]{\texttt\{\meta{#1}\texttt\}}


\providecommand\eTeX{\hologo{eTeX}}
\providecommand\XeTeX{\hologo{XeTeX}}
\providecommand\LuaTeX{\hologo{LuaTeX}}
\providecommand\pdfTeX{\hologo{pdfTeX}}
\providecommand\MiKTeX{\hologo{MiKTeX}}
\providecommand\CTAN{\textsc{ctan}}
\providecommand\TL{\TeX\,Live}
\providecommand\githubissue[2][]{\ifhmode\unskip\fi
     \quad\penalty500\strut\nobreak\hfill
     \mbox{\small\slshape(%
       \href{https://github.com/latex3/latex2e/issues/\getfirstgithubissue#2 \relax}%
          	    {github issue#1 #2}%
           )}%
     \par\smallskip}
%% But Chris has to mostly disable \href for his TEXPAD app:
%%  \def\href #1{}  % Only For Chris' deficient TeX engine

% simple solution right now (just link to the first issue if there are more)
\def\getfirstgithubissue#1 #2\relax{#1}

\providecommand\sxissue[1]{\ifhmode\unskip
     \else
       % githubissue preceding
       \vskip-\smallskipamount
       \vskip-\parskip
     \fi
     \quad\penalty500\strut\nobreak\hfill
     \mbox{\small\slshape(\url{https://tex.stackexchange.com/#1})}\par}

\providecommand\gnatsissue[2]{\ifhmode\unskip\fi
     \quad\penalty500\strut\nobreak\hfill
     \mbox{\small\slshape(%
       \href{https://www.latex-project.org/cgi-bin/ltxbugs2html?pr=#1\%2F\getfirstgithubissue#2 \relax}%
          	    {gnats issue #1/#2}%
           )}%
     \par}

\let\cls\pkg
\providecommand\env[1]{\texttt{#1}}
\providecommand\acro[1]{\textsc{#1}}

\vbadness=1400  % accept slightly empty columns


\makeatletter
% maybe not the greatest design but normally we wouldn't have subsubsections
\renewcommand{\subsubsection}{%
   \@startsection      {subsubsection}{2}{0pt}{1.5ex \@plus 1ex \@minus .2ex}%
      {-1em}{\@subheadingfont\colonize}%
}
\providecommand\colonize[1]{#1:}

\renewcommand{\contentsname}{目录 Contents}
\renewcommand{\maketitle}{%
   \twocolumn[{%
      \parbox[t][7\baselineskip]{\textwidth}{%
         \@titlefont\@title\\[\medskipamount]
         \normalfont\normalsize\issuename~\@issue, \@year~年~\@month~月
      }%
   }]%
   \thispagestyle{titlepage}
}
\newcommand*\thbox{\texorpdfstring\hbox{}}
\makeatother

\let\finalvspace\vspace          % for document layout fixes

% Undo ltnews's \verbatim@font with active < and >
\makeatletter
\def\verbatim@font{%
  \normalsize\ttfamily}
\makeatletter

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\providecommand\tubcommand[1]{}
\tubcommand{\input{tubltmac}}

\publicationmonth{6}
\publicationyear{2022}

\publicationissue{35}

\def\TEX{\TeX}
\def\LATEX{\LaTeX}
\def\LATEXe{\LaTeXe}

\newcommand{\itransnote}[1]{（{\bfseries \textit{译者注：}#1}）}
\newcommand{\transnote}[1]{\par{\bfseries \textit{译者注：}#1}\par}

\usepackage{indentfirst}
\setlength{\parindent}{1.1em}

\SetKeys[hyp/setup]{pdfauthor={The LaTeX Project, translated by Longaster}, 
  pdftitle={LaTeX2e Released 2022-06-01 News (LaTeX News 35)}}

\renewcommand{\LaTeXNews}{\LaTeX~动态，\LaTeX~News}

\begin{document}

\tubcommand{\addtolength\textheight{4.2pc}}   % only for TUB

\maketitle
{\raggedright \hyphenpenalty=10000 \exhyphenpenalty=10000 \spaceskip=3.33pt \hbadness=10000
\tableofcontents}

\setlength\rightskip{0pt plus 3em}


\medskip


\section{引言 Introduction}

2022 年 6 月发布的 \LATEX{} 再次专注于为我们的多年项目所做的改进，以自动提供标记的 PDF 输出
\cite{35:blueprint}。新的文档元数据接口，新的 mark 机制，选项的标准键值设置方法，
引入了 \texttt{latex-lab} 包，它用于保存那些能被文档可选的加载的内容
（当 \cs{DocumentMetadata} 使用特定的键值选项时加载）。
本文第一节描述了具体细节。与这项工作相关的是 \pkg{hyperref} 和 \pkg{tagpdf} 的更新，
它们在各自的发行版中均有描述。

\begin{english}
The 2022 June release of \LaTeX{} is again focussing on improvements
made for our multi-year project to automatically offer tagged PDF
output~\cite{35:blueprint}. These are the new document metadata
interface, the new mark mechanism for \LaTeX{}, a standard key/value
approach for options, and the introduction of the \texttt{latex-lab}
area for temporary code that can be optionally loaded by a document
(when \cs{DocumentMetadata} is used with certain test keys). These
additions are described in the first sections.  Related to this effort
there are updates to \pkg{hyperref} and \pkg{tagpdf}, both of which
have their own distributions.
\end{english}

正如往常一样，我们也增加了一些小的改进，修复了 \LaTeX{} 内核中的一些问题。
可能令人最感兴趣的（对某些用户来说）是：直接支持浮点运算（通过 \cs{fpeval}，见下）
和正确对公式着色而不出现间距问题。为此我们提供了 \cs{mathcolor}；见本文末。
现在 \pkg{doc} 宏包支持更精细的代码元素分类，同时也正确的支持 \pkg{hyperref} 了。

\begin{english}
As usual, we also added a number of smaller improvements and bug
fixes in various components of core \LaTeX{}. Perhaps the most
interesting ones (for some users) are direct support for floating
point arithmetic (via \cs{fpeval}; see below) and the ability to
properly color parts of math formulas without introducing spacing
problems. For this we now offer the command \cs{mathcolor}; see the
description near the end of the newsletter.  There is also a new major
release of the \pkg{doc} package that supports a more fine-grained
classification of code elements and properly supports \pkg{hyperref}.
\end{english}

\transnote{%
本次更新是一次较大的更新，通过使用 \cs{DocumentMetadata}，新的 generic driver 可以使用，
此驱动为 PDF 资源、标记（annot）、表单的创建和使用提供了统一的接口（\LaTeX3 接口），
最明显的是 \XeTeX{} 能解决跨页颜色和透明度的问题了，原来只有在 PDF 模式下才能使用的宏包，
使用新的接口修改后可同时用于多种引擎中。

使用此驱动，\XeTeX{} 也能获取外部 PDF 的资源，这样导入的外部 PDF 中的超链接在当前文档
仍然可用。此外还有其它功能，这里不再叙述。

另外，原有的 mark 机制也得到了更新，使用 \eTeX{} 提供的寄存器来更新 mark，同时也能得到
不同存储域中 mark 的内容，而不限于当前整页的 mark。也提供了标记、获取、比较 mark 的接口。

\LaTeX{} 内核原生支持键值选项了！（主要使用 \LaTeX3 的 \pkg{l3keys}）。
}

\section{文档元数据接口 Document metadata interface}

直到最近，还没有专门的位置来声明影响整个文档的设置。设置必须放在序言中的某个地方，
或者作为类选项，有时甚至作为宏包选项。对于某些此类设置，这可能会导致问题，
例如，只有在要生成的 PDF 文件尚未打开时才能设置 PDF 版本，
而这可能由于加载某个宏包而发生（从而后续设置 PDF 版本无效）。

\begin{english}
Until recently there was no dedicated location to declare
settings that affect a document as a whole. Settings had to be placed
somewhere in the preamble or as class options or sometimes even as
package options. For some such settings this may cause issues, e.g.,
setting the PDF version is only possible as long as the PDF output
file has not yet been opened which can be caused by loading one or the
other package.
\end{english}

对 \enquote{\LaTeX{} Tagged PDF project} ~\cite{35:blueprint} 项目来说，
需要考虑整个文档的元数据及其处理，这样的数据应该被放置在某个设计好的位置。

\begin{english}
For the \enquote{\LaTeX{} Tagged PDF project}~\cite{35:blueprint}
further metadata about the whole document (and its processing) need to
be specified and again this data should be all placed in a single
well-defined place.
\end{english}

由于这些原因，我们引入 \cs{DocumentMetadata} 命令来在一个位置统一设置这些元数据。
这个命令接收描述文档元数据的键值对，它作用于当前文档。
这个命令仅能使用在文档的最开始处，即必须\emph{先于} \cs{documentclass}，否则将报错。

\begin{english}
For this reason we introduce the new command \cs{DocumentMetadata} to
unify all such settings in one place.  The command expects a key/value
list that describes all document metadata for the current document. It
is only allowed to be used at the very beginning of the document,
i.e., the declaration has to be placed \emph{before}
\cs{documentclass} and will issue an error if found later.
\end{english}

此时，我们仅在内核中提供很少的命令，这些键值对的处理方式在外部定义%
\itransnote{加载其它宏包和文件}，当这个命令被使用时才加载所需的代码。
使用此机制出于两个原因：一是，添加此命令在内核中可无需使用 \cs{RequirePackage} 即可使用它们。
二是，实际处理的代码在外部文件（而不是在内核中）可以让我们在上述项目推进时
方便地对其扩展和修改。此二者允许用户立即受益于作为项目一部分产生的中间结果，
同时也使得 \LaTeX{} 项目团队有更多的灵活性，让这样的中间结果独立于定期的 \LaTeX{} 发行版。
随着时间的推移，经过测试和批准的功能可以在稍后阶段无缝地移动到内核中，而无需对已经使用
它的文档进行任何更改。同时，不使用新的整合界面意味着现有文档不会受到正在执行的
处于更广泛的 alpha 或 beta 测试阶段的工作的影响，

\begin{english}
At this point in time we provide only the bare command in the format;
the actual processing of the key/value is defined externally and the
necessary code will be loaded if the command is used. This scheme is
chosen for two reasons: by adding the command in the kernel it is
available to everybody without the need to load a special package
using \cs{RequirePackage}. The actual processing, though, is external
so that we can easily extend the code (e.g., offering additional keys
or changing the internal processing) while the above-mentioned project
is progressing. Both together allows users to immediately benefit from
intermediate results produced as part of the project, as well as
offering the \LaTeX{} Project Team the flexibility to enable such
intermediate results (for test purposes or even production use)
in-between and independently of regular \LaTeX{} releases. Over time,
tested and approved functionality can then seamlessly move into the
kernel at a later stage without any alterations to documents already
using it. At the same time, not using the new consolidated interface
means that existing documents are in no way affected by the work that
is carried out and is in a wider alpha or beta test phase.
\end{english}

关于这个新命令以及已有的键值选项的文档包含在 \file{l3meta.pdf} 及
\file{documentmetadata-support.pdf} 中，同时也在 \pkg{pdfmanagement-testphase}
宏包文档中。

\begin{english}
Documentation about the new command and
already existing keys are in \file{l3meta.pdf} and \file{documentmetadata-support.pdf}
and also in the documentation of the \pkg{pdfmanagement-testphase} package.
\end{english}

宏包和文档作者能使用 \cs{IfDocumentMetadataTF} 判断用户是否已使用 \cs{DocumentMetadata}。

\begin{english}
Package and class authors can test if a user has used \cs{DocumentMetadata}
with \cs{IfDocumentMetadataTF}.
\end{english}


\section{\pkg{latex-lab} 包, The \pkg{latex-lab} bundle}

我们添加了一个新的 latex-laboratory 包（bundle），我们在其中放置了只能通过
\cs{DocumentMetadata} 声明使用的新代码，而且最重要的是，它正在开发中，如有更改，
将不会另行通知。这意味着那里提供的命令和接口可能会在一些公开测试后再次被更改或删除。 
可以通过 \cs{DocumentMetadata} 的 \texttt{testphase} 键访问代码。
当前支持的值是标记的 PDF 项目（tagged PDF project）的代码的阶段 I 和阶段 II
（阶段 I 被冻结，阶段 II 是我们当前正在处理的阶段）。使用
\begin{verbatim}
  \DocumentMetadata{testphase=phase-II}
\end{verbatim}
将启用对段落和脚注的标记；更多文档元素将持续跟进。

\begin{english}
We added a new \pkg{latex-lab}oratory bundle in which we place new
code that is going to be available only through a
\cs{DocumentMetadata} declaration and that is\Dash most
importantly\Dash work under development and subject to
change without further notice. This means that commands and interfaces 
provided there mayget altered or removed again after some public testing.
The code can be accessed through the \cs{DocumentMetadata} key \texttt{testphase}.
Currently supported values are \texttt{phase-I} and \texttt{phase-II}
that enable code of the tagged PDF project (phase~I is frozen, and
phase~II is the phase we are currently working on).  With
\begin{verbatim}
  \DocumentMetadata{testphase=phase-II}
\end{verbatim}
you currently enable tagging for paragraphs and footnotes; more
document elements will follow soon.
\end{english}

最终，代码将从测试阶段（一旦被认为是稳定的）移动到 \LATEX{} 内核。
标记将继续需要 \cs{DocumentMetadata} 声明，但您将能够删除 \texttt{testphase} 键的设置。

\begin{english}
Eventually, code will move (once considered stable) from the
testphase into the \LaTeX{} kernel itself. Tagging will continue to
require a \cs{DocumentMetadata} declaration, but you will then be able
to drop the \texttt{testphase} key setting.
\end{english}


\section{\thbox{新的 mark 机制} A new mark mechanism for \LaTeX{}}

mark 机制是 TeX 将信息传递给页面构建过程的方式，该过程异步发生，以便将执行时
页眉和页脚的相关数据传达给后者，例如，页面上的第一部分或最后一个小节是什么，等等。
但是，标记也可以用于其他目的。新的内核模块为独立类的标记提供了一种通用机制。

\begin{english}
The mark mechanism is \TeX{}'s way to pass information to the
page-building process, which happens asynchronously, in order to
communicate relevant data for running headers and footers to the
latter, e.g., what is the first section on the page or the last
subsection, etc. However, marks may also be
used for other purposes. The new kernel module provides a generalized
mechanism for marks of independent classes.
\end{english}

\TeX{} 引擎提供了一种 low-level 的标记机制来将有关当前页面内容的信息传递给异步操作输出例程。
它通过将 \cs{mark} 命令放入源文档来工作。

\begin{english}
The \TeX{} engines offer a low-level mark mechanism to
communicate information about the content of the current page to
the asynchronous operating output routine. It works by placing
\cs{mark} commands into the source document.
\end{english}

这种机制适用于仅调用输出例程来生成页面的简单格式（例如 plain \TeX）。
然而，在 \LATEX （和其他更复杂的格式）中它会失败，因为这里有时会调用输出例程而不产生页面，
例如，当遇到一个浮动体并将其放入一个浮动区域时。
当这种情况发生时，\TeX{} 的 \cs{topmark} 不再反映下一页最终被构造时的情况。

\begin{english}
This mechanism works well for simple formats (such as plain \TeX)
whose output routines are only called to generate pages. It
fails, however, in \LaTeX{} (and other more complex formats),
because here the output routine is sometimes called without
producing a page, e.g., when encountering a float and placing it
into one of the float regions.
%
When that happens \TeX{}'s  \cs{topmark} no
longer reflects the situation at the top of the next page when that
page is finally boxed.
\end{english}

此外，\TEX{} 只提供一个标记，而 \LATEX{} 想要跟踪多条信息。
出于这个原因，\LATEX 实现了自己的标记机制，其中标记总是包含两个部分，它们有自己的接口：
\cs{markboth} 和 \cs{markright} 来设置标记，\cs{leftmark} 和 \cs{rightmark} 来检索它们。

\begin{english}
Furthermore, \TeX{} only offered a single mark while \LaTeX{} wanted to
keep track of more than one piece of information.  For that reason,
\LaTeX{} implemented its own mark mechanism where the marks always
contained two parts with their own interfaces: \cs{markboth} and
\cs{markright} to set marks and \cs{leftmark} and \cs{rightmark} to
retrieve them.
\end{english}

不幸的是，这种扩展机制虽然支持章/节标记等场景，但远非通用。
页面顶部的标记情况（即 \cs{topmark}）仍然无法使用，并且提供的两个标记并不是真正相互独立的，
因为 \cs{markboth}（如名称所示）总是设置两者。

\begin{english}
Unfortunately, this extended mechanism, while supporting scenarios such
as chapter/section marks, was far from general. The mark
situation at the top of a page (i.e., \cs{topmark}) remained
unusable and the two marks offered were not really independent of
each other because \cs{markboth} (as the name indicates) was
always setting both.
\end{english}

开始于 2022 的年发行版，现在在 \LaTeX{} 中可用的新机制解决了如下问题：

\begin{english}
The new mechanism now available in \LaTeX{} starting with the 2022
release overcomes both issues:
\end{english}

\begin{itemize}
\item 提供了任意多个\itransnote{实际有上限}，完全独立的具名标记（named marks），它能在分配后一直使用。
\begin{english}
\item
  It provides arbitrary many, fully independent named marks, that
  can be allocated and from that point onwards used.
\end{english}
\item 提供了获得这样的标记的 top、first、bottom 值的接口。
\begin{english}
\item
  It offers access for each such mark to retrieve its top,
  first, and bottom value separately.
\end{english}
\item 此外，该机制得到了增强，可以访问不同“区域”中的标记，这些“区域”可能不是整个页面。
\begin{english}
\item
  Furthermore, the mechanism is augmented to give access to marks
  in different ``regions'', which may be other than full pages.
\end{english}
\end{itemize}

旧的接口，例如，\cs{markboth}，仍然保留下来了。
因此，使用它们的类和包继续无缝工作。为了利用扩展的可能性，现在还可以使用一组新的命令来声明
标记类、设置它们的值和查询它们的状态（在输出例程中）。
您可以在文件 \texttt{ltmarks-doc.pdf} 中找到新接口的文档以及有关机制的示例和进一步说明。
只需在终端中执行 \texttt{texdoc} \texttt{ltmarks-doc} 即可在您的计算机上显示它。

\begin{english}
The legacy interfaces, e.g., \cs{markboth}, are kept. Thus classes and
packages making use of them continue to work seamlessly. To make use
of the extended possibility a new set of commands for the declaration of
mark classes, setting their values and querying their state (in the
output routine) is now available in addition.
%
You find the documentation for the new interfaces together with
examples and further notes on the mechanism in the file
\texttt{ltmarks-doc.pdf}. Just call \texttt{texdoc}
\texttt{ltmarks-doc} to display it on your computer.
\end{english}

\transnote{\eTeX{} 时代的 mark 寄存器终于被使用了！}


\section{\thbox{键值选项} A key/value approach to option handling}

\LaTeX{} 中处理选项的经典方法是使用 \cs{ProcessOptions}，将列表中的每个条目视为一个字符串。
许多包作者试图通过将每个条目视为键值对（keyval）来扩展这种处理。
迄今为止，这需要使用额外的软件包，例如 \pkg{kvoptions}。

\begin{english}
The classical \LaTeXe{} method for handling options, using \cs{ProcessOptions},
treats each entry in the list as a string. Many package authors have sought to
extend this handling by treating each entry as a key--value pair (keyval)
instead. To date, this has required the use of additional packages, for example
\pkg{kvoptions}.
\end{english}

一段时间以来，\LATEX{} 团队一直提供包 \pkg{l3keys2e} 以允许使用 L3 编程层模块 \pkg{l3keys} 
定义的键值作为包选项。此功能现在已直接集成到内核中。作为此集成的一部分，
处理键值选项的语法已经过改进，例如 \cs{ProcessKeyOptions} 将自动获取当前宏包名作为
\emph{family}，除非显示指定可选值：
\begin{verbatim}
\ProcessKeyOptions[family]
\end{verbatim}

\begin{english}
The \LaTeX{} team have for some time offered the package \pkg{l3keys2e} to
allow keyvals defined using the L3 programming layer module \pkg{l3keys} to act
as package options. This ability has now been integrated directly into the
kernel. As part of this integration, the syntax for processing keyval options
has been refined, such that
\begin{verbatim}
\ProcessKeyOptions
\end{verbatim}
will now automatically pick up the package name as the key \emph{family},
%unless explicitly given as an optional argument.
unless explicitly given as an optional argument:
\begin{verbatim}
\ProcessKeyOptions[family]
\end{verbatim}
\end{english}

为了支持为此机制创建密钥选项，添加了新命令 \cs{DeclareKeys}。
这使用与 \pkg{l3keys} 或 \pkg{pgfkeys} 相同的通用方法工作：
每个键都有一个或多个定义其行为的\emph{属性}。

\begin{english}
To support creating key options for this mechanism, the new command
\cs{DeclareKeys} has been added. This works using the same general
approach as \pkg{l3keys} or \pkg{pgfkeys}: each key has one or more
\emph{properties} which define its behavior.
\end{english}

内核不会检查使用这种新方法的宏包选项是否存在冲突。
相反，每次遇到 \cs{usepackage} 或 \cs{RequirePackage} 行时，给出的选项列表将被传递给
\cs{ProcessKeyOptions}。只能在第一次加载包时给出的选项可以使用属性 \texttt{.usage = load}
进行标记，如果在后续的包加载行中使用将导致警告。

\begin{english}
Options for packages which use this new approach will not be checked for
clashes by the kernel. Instead, each time a \cs{usepackage} or
\cs{RequirePackage} line is encountered, the list of options given will be
passed to \cs{ProcessKeyOptions}. Options which can only be given
the first time a package is loaded can be marked using the property
\texttt{.usage = load}, and will result in a warning if used in a subsequent
package loading line.
\end{english}

以这种方式定义的宏包选项也可以在宏包中使用新命令 \cs{SetKeys} 进行设置，
该命令再次采用一个可选参数来指定其 \emph{family}，加上选项本身的必须参数。

\begin{english}
Package options defined in this way can also be set within a package using
the new command \cs{SetKeys}, which again takes an optional argument
to specify the \emph{family}, plus a mandatory one for the options themselves.
\end{english}


\section{新的或改进的命令 New or improved commands}


\subsection{\thbox{浮点和整数计算} Floating point and integer calculations}

原来由 \pkg{xfp} 提供的 \cs{fpeval} 和 \cs{inteval} 现在集成进内核中，同时还提供了
\cs{dimeval} 和 \cs{skipeval}。

\begin{english}
The L3 programming layer offers expandable commands for calculating
floating point and integer values, but so far these functions have
only been available to programmers, because they require
\cs{ExplSyntaxOn} to be in force. To make them easily available at the
document level, the small package \pkg{xfp} defined \cs{fpeval} and
\cs{inteval}.


An example of use could be the following:
\begin{verbatim}
  \LaTeX{} can now compute:
  \[ \frac{\sin (3.5)}{2} + 2\cdot 10^{-3}
      = \fpeval{sin(3.5)/2 + 2e-3}         \]
\end{verbatim}
which produces the following output:
\begin{quote}
\LaTeX{} can now compute:
\[ \frac{\sin (3.5)}{2} + 2\cdot 10^{-3}
   = \fpeval{sin(3.5)/2 + 2e-3}         \]
\end{quote}
These two commands have now been moved into the kernel and in addition
we also provide \cs{dimeval} and \cs{skipeval}. The details of their
syntax are described in \file{usrguide3.pdf}.  The command \cs{fpeval}
offers a rich syntax allowing for extensive calculations, whereas the
other three commands are essentially thin wrappers for \cs{numexpr},
\cs{dimexpr}, and \cs{glueexpr} \Dash therefore inheriting some syntax
%peculiars and limitations in expressiveness.
peculiarities and limitations in expressiveness.
%  \newcommand\calulateheight[1]{%
\begin{verbatim}
  \newcommand\calculateheight[1]{%
    \setlength\textheight{\dimeval{\topskip
          + \baselineskip * \inteval{#1-1}}}}
\end{verbatim}
The above, for example, calculates the appropriate \cs{textheight} for
a given number of text lines.
%
\githubissue{711}
\end{english}


\subsection{改变参数的驼峰式命令 CamelCase commands for changing arguments to csnames}

提供了 \cs{ExpandArgs} 命令来控制展开方式，它与 \LaTeX3 中的 \cs{exp\_args:N...} 对应。

\begin{english}
It is sometimes helpful to \enquote{construct} a command name on the
fly rather than providing it as a single \cs{...}\ token. For these
kinds of tasks the \LaTeX3 programming layer offers a general mechanism
(in the form of \cs{exp\_args:N...}\ and
\cs{cs\_generate\_variant:Nn}). However, when declaring new
document-level commands with \cs{NewDocumentCommand} or
\cs{NewCommandCopy}, etc.\ the L3 programming layer may not be active,
and even if it is, mixing CamelCase syntax with L3 programming syntax
is not really a good approach. We have therefore added the commands
\cs{UseName} and \cs{ExpandArgs} to assist in such
situations, e.g.,
\begin{verbatim}
\NewDocumentCommand\newcopyedit{mO{red}}
  {\newcounter{todo#1}%
   \ExpandArgs{c}\NewDocumentCommand{#1}{s m}%
     {\stepcounter{todo#1}%
      \IfBooleanTF {##1}%
         {\todo[color=#2!10]%
            {\UseName{thetodo#1}: ##2}}%
         {\todo[inline,color=#2!10]%
            {\UseName{thetodo#1}: ##2}}%
     }%
  }
\end{verbatim}
which provides a declaration mechanism for copyedit commands, so that
\verb=\newcopyedit{FMi}[blue]= then defines \cs{FMi} (and the
necessary counter).

The command \cs{ExpandArgs} can be useful with the argument \texttt{cc} or
\texttt{Nc} in
combination with \cs{NewCommandCopy} if the old or new command name
or both need constructing. Finally, there is \cs{UseName} which
takes its argument and turns it into a command (i.e., a CamelCase
version of \cs{@nameuse} (\LaTeXe) or \cs{use:c} (L3 programming
layer)) which was also used in the example above.
%
\githubissue{735}
\end{english}


\subsection{\thbox{测试几乎为空的参数} Testing for (nearly) empty arguments}

提供了 \cs{IfBlankTF}、\cs{IfBlankT}、\cs{IfBlankF} 来测试参数是否为空白
\itransnote{即，完全为空或仅包含空格}。

\begin{english}
%
In addition to \cs{IfNoValueTF} to test if an optional argument was
provided or not, there is now also \cs{IfBlankTF}, which tests if the
argument is empty or contains only blanks. Based on the result it
selects a true or false code branch. As usual, the variants
\cs{IfBlankT} and \cs{IfBlankF} are also provided for use when only one
branch leads to some action.  Further details and examples are given
in \file{usrguide3.pdf}.

This test can also be useful if you set up key/value options and want
to test if a key was specified without giving a value, vs.\ 
specifying \enquote{\textit{key}\texttt{ = ,}}.
\end{english}


\subsection{Better allocator for Lua command ids}

In \LuaTeX\ we already had the \cs{newluafunction} macro which allocates
a Lua function identifier which can be used to define commands
with \cs{luadef}. But this always required two steps: \cs{newluafunction}
defines the passed control sequence as an integer, which then has to be used
to define the actual Lua command with \cs{luadef}. After that, the integer is
no longer needed. This was inconsistent with other allocators. Therefore we
added two new allocators \cs{newluacmd} and \cs{newexpandableluacmd} which
directly define a control sequences invoking the allocated Lua function.
The former defines a non-expandable Lua command, the latter an expandable
one. Of course, the associated Lua function still has to be defined by assigning
a function to the \verb|lua.get_functions_table()| table. The required index is
available in \cs{allocationnumber}.

An example could be
\begin{verbatim}
\newluacmd \greeting
\directlua {
lua.get_functions_table()
   [tex.count.allocationnumber]
   = function()
    local name = token.scan_argument()
    tex.sprint('Hello ', name, '!')
  end
}
\greeting{world}
\end{verbatim}
%
\githubissue{536}

\subsection{Starred command version for \cs{ref}, \cs{Ref} and \cs{pageref}}

For a long time \pkg{hyperref} has provided starred versions for the reference commands
which do not create active links. This syntax extension required users and
package authors to check if \pkg{hyperref} was loaded and adjust the coding
accordingly or take the starred forms out if text was copied to a document
without \pkg{hyperref}. The commands have now been aligned with
the \pkg{hyperref} usage and always allow an optional star. The \pkg{showkeys} package
has been updated to handle the starred versions too, both with \pkg{hyperref} or \pkg{nameref}
and without. The commands are defined with \cs{NewDocumentCommand} and so no longer expand when
written to auxiliary files. This reduces the number of compilations needed to resolve references
in captions and sectioning commands. The package \pkg{ifthen} has been updated to ensure that
\cs{pageref} can still be used inside tests like \cs{isodd}.


\subsection{\thbox{为后端支持 PDF 做准备} Preparation for supporting PDF in backends}

At the current point in time, basic support for PDF in
backends is not part of \LaTeX{} core; it is provided by an external
package like \pkg{hyperref}.
At some time in the future that work will be placed
into the kernel but for now it is separate and has to be
explicitly loaded in the document. To enable class and package authors
to support PDF-specific tasks like the creation of link targets without
having to test first if \pkg{hyperref} has been loaded, dummy versions of
the commands \cs{MakeLinkTarget}, \cs{LinkTargetOn}, \cs{LinkTargetOff} and
\cs{NextLinkTarget} are provided.

\section{代码改进 Code improvements}

\subsection{\cs{protected} UTF-8 character definitions}
The characters defined via \file{utf8.def} are now defined as \cs{protected}
macros. This makes them safe to use in expansion contexts where the
classic \cs{protect} mechanism is not enabled, notably L3 programming
layer \texttt{e} and \texttt{x} arguments.

Related to this change \cs{MakeUppercase} and \cs{MakeLowercase} have
been updated to use the Unicode-aware case changing functions
\cs{text\string_lowercase:n} in place of the \TeX\ primitive \cs{lowercase}.
A similar change will be made in the \pkg{textcase} package.

Note: for technical reasons these low-level character handling changes
will not be rolled back if the format version is rolled back using the
\pkg{latexrelease} package rollback mechanism.
%
\githubissue{780}

\subsection{\thbox{对 \cs{obeylines} 和 \cs{obeyedspace} 的小改进} A small update to \cs{obeylines} and \cs{obeyspaces}}

The plain \TeX{} versions of \cs{obeylines} and \cs{obeyspaces} make
\verb=^^M= and \verb*= = active and force them to execute \cs{par} %*
and \cs{space}, respectively. Don Knuth makes a remark in the \TeX{}book
that one can then use a trick such as
\begin{verbatim}
  \let\par=\cr \obeylines \halign{...
\end{verbatim}
However, redefining \cs{par} like this 
may lead to all kinds of problems in \LaTeX. We have therefore changed
the commands to use an indirection: the active characters now execute
\cs{obeyedline} and \cs{obeyedspace}, which in turn do what the
hardwired solution did before.

\begin{quote}
  \renewcommand\obeyedspace{\ \textbullet\ }
  \footnotesize\obeyspaces%
This means that it is now possible to %
achieve special effects in a safe way. %
This paragraph, for example, was produced by %
making \cs{obeyedspace} generate %
\texttt{\{\cs{\verbvisiblespace}\cs{textbullet}\cs{\verbvisiblespace}\}} and %
enabling \cs{obeyspaces} within a %
quote environment.
\end{quote}
Thus, if you are keen to use the plain \TeX{} trick, you need to say
\cs{let}\cs{obeyedlines}\texttt{=}\cs{cr} now.
%
\githubissue{367}


\subsection{\thbox{\pkg{doc} 宏包更新到版本 3}, \pkg{doc} upgraded to version~3}

After roughly three decades the \pkg{doc} package received a cautious
uplift, as already announced at the 2019 TUG conference\Dash changes
to \pkg{doc} are obviously always done in a leisurely manner.

Given that most documentation is nowadays viewed on screen,
\pkg{hyperref} support is added and by default enabled (suppress it
with option \option{nohyperref} or alternatively with
\option{hyperref}\texttt{=false}) so the internal cross-references are
properly resolved including those from the index back into the
document.

Furthermore, \pkg{doc} now has a general mechanism to define
additional \enquote{doc} elements besides the two \texttt{Macro} and
\texttt{Env} it has known in the past. This enables better
documentation because you can now clearly mark different types of
objects instead of simply calling them all \enquote{macros}.
If desired, they can be collected together under a heading
in the index so that you have a section just with your document
interface commands, or with all parameters, or \ldots

The code borrows ideas from Didier Verna's \pkg{dox} package (although
the document level interface is different) and it makes use of Heiko
Oberdiek's \pkg{hypdoc} package, which at some point in the future
will be completely integrated, given that its whole purpose it to
patch \pkg{doc}'s internal commands to make them \pkg{hyperref}-aware.

All changes are expected to be upward compatible, but if you run into
issues with older documentation using \pkg{doc} a simple and quick
solution is to load the package as follows:
\verb/\usepackage{doc}[=v2]/

\subsection{\pkg{doc} 宏包现在能在版本历史中显示日期了, \pkg{doc} can now show dates in change log}

Up to now the change log was always sorted by version numbers
(ignoring the date that was given in the \cs{changes} command).  It
can now be sorted by both version and date if you specify the option
\option{reportchangedates} on package level and in that case the
changes are displayed with
\begin{quote}
  \meta{version} -- \meta{date}
\end{quote}
as the heading (instead of just \meta{version}), when using
\cs{PrintChanges}.
%
\githubissue{531}



\subsection{\class{ltxdoc} gets options \option{nocfg} and \option{doc2}}

The \LaTeX{} sources are formatted with the \class{ltxdoc} class,
which supports loading a local config file \file{ltxdoc.cfg}. In the
past the \LaTeX{} sources used such a file but it was not distributed.
As a result reprocessing the \LaTeX{} sources elsewhere showed
formatting changes.  We now distribute this file which means that it
is loaded by default. With the option \option{nocfg} this can be
prevented.

We also added a \option{doc2} option to the class so that it is
possible to run old documentation with \pkg{doc} version~2, if
necessary.



\subsection{Lua\TeX\ callback improvements}

The Lua\TeX\ callbacks \texttt{hpack\_quality} and \texttt{vpack\_quality} are
now \texttt{exclusive} and therefore only allow a single handler.
The previous type \texttt{list} resulted in incorrect parameters when multiple
handlers were set; therefore, this only makes an existing restriction more
explicit.

Additionally the return value \texttt{true} for \texttt{list}
callbacks is now handled internally and no longer passed on to the
engine. This simplifies the handling of these callbacks and makes it
easier to provide consistent interfaces for user-defined \texttt{list}
callbacks.


\subsection{Class \class{proc} supports \option{twoside}}

The document class \class{proc}, which is a small variation on the
\class{article} class, now supports the \option{twoside} option,
displaying different data in the footer line on recto and verso pages.
%
\githubissue{704}


\subsection{Croatian character support}

The default \pkg{inputenc} support has been extended to support the 9 characters
D\v Z, D\v z, d\v z, LJ, Lj, lj, NJ, Nj, nj, input as single UTF-8 code points
in the range U+01C4 to U+01CC.
%
\githubissue{723}


\subsection{Cleanup of the Unicode declaration interface}

When declaring encoding specific commands for the Unicode (TU)
encoding some declarations (e.g., \cs{DeclareUnicodeComposite}) do not
have an explicit argument for the encoding name, but instead use
the command \cs{UnicodeEncodingName} internally. There was one
exception though: \cs{DeclareUnicodeAccent} required an explicit
encoding argument.  This inconsistency has now been removed and the
encoding name is always implicit. To avoid a breaking change for a few
packages on CTAN, \cs{DeclareUnicodeAccent} still accepts three
arguments if the second argument is \texttt{TU} or
\cs{UnicodeEncodingName}. Once all packages have been updated this
code branch will get removed.

At the same time we added \cs{DeclareUnicodeCommand} and
\cs{DeclareUnicodeSymbol} for consistency. They also use
\cs{UnicodeEncodingName} internally, instead of requiring an encoding
argument as their general purpose counterparts do.
%
\githubissue{253}


\subsection{新钩子 New hook:\ \hook{include/excluded}}

A few releases ago we introduced a number of file hooks for different
types of files; see~\cite{35:ltnews32} and in
particular~\cite{35:ltfilehook-doc}.
%
The hooks for \cs{include} files now have an addition: if such a file
is not included (because \cs{includeonly} is used and its \meta{name}
is not listed in the argument) then the hooks \hook{include/excluded}
and \hook{include/\meta{name}/excluded} are executed in that
order\Dash of course, only if they contain code.  This happens after
\LaTeX{} has loaded the \texttt{.aux} file for this include file,
i.e., after \LaTeX{} has updated its counters to pretend that the file
was seen.


\subsection{Input support for normalized angle brackets}

Source files containing \textlangle\ or \textrangle\ directly written
as Unicode codepoints U+2329 and U+232A no longer break when the
source file gets normalized under Unicode normalization rules.
%
\githubissue{gh/714}




\section{Bug 修复 Bug fixes}

\subsection{Using \cs{DeclareUnicodeCharacter} with C1 control points}
An error in the UTF-8 handling for non-Unicode \TeX\ has prevented
\cs{DeclareUnicodeCharacter} being used with characters in the range
hex 80 to 9F. This has been corrected in this release.
%
\githubissue{730}



\subsection{Fix \cs{ShowCommand} when used with \pkg{ltcmd}}

When \cs{ShowCommand} support was added for \pkg{ltcmd} in the previous
release~\cite{35:ltnews34}, a blunder in the code made it so that
when \cs{ShowCommand} was used on a command defined with \pkg{ltcmd}, it
only printed the meaning of the command in the terminal, but didn't stop
for interaction as it does elsewhere (mimicking \cs{show}).  The issue
is now fixed.
%
\githubissue{739}



\subsection{Make \cs{cite}\texttt{\textbraceleft\textbraceright} produce a warning}

When the \cs{cite} command can't resolve a citation label it issues a
warning \enquote{Citation `\meta{label}' on page \meta{page}
  undefined}.  However, due to some implementation details a completely
empty argument was always silently accepted. Given that there are probably
people who write \verb=\cite{}= with the intention to fill in the
correct label later it is rather unfortunate if that is not generating
a warning that something in the document is still amiss.
This has finally been corrected and a warning is now generated also in this case.
%
\githubissue{790}



\subsection{Fix adding \hook{cmd} hooks to simple macros}

A bug in how \LaTeX{} detected the type of a command caused a
premature forced expansion of such commands, which, depending on their
definition, could be harmless or could cause severe trouble.  This has
been fixed in the latest release.
%
\githubissue{795}
\sxissue{q/637565}


\subsection{Warn if \hook{shipout/lastpage} hook is executed too early}

The hook \hook{shipout/lastpage} is intended to place \cs{special}s
into the last page shipped out. This is needed for some use cases,
e.g., tagging. If that hook is nonempty and the user has added additional
pages since the last run, then \LaTeX{} executes this hook too early,
but until now without giving any indication that the document needs
rerunning. This has now been corrected and an appropriate warning is
given.
%
\githubissue{813}


\subsection{More consistent use of cramped math styles in \LuaTeX}

Using \LuaTeX's \cs{Udelimiterover} to place a horizontally extensible glyph
on top of a mathematical expression now causes the expression to be set in cramped
style, as used in similar situations by traditional \TeX\ math rendering.
Similarly, cramped style is now used for expressions set under such a delimiter
using \cs{Uunderdelimiter}, but is no longer used when setting an expression on top
of such extensible glyphs using \cs{Uoverdelimiter}.
This new behavior follows \TeX's rule that cramped style is used whenever something
else appears above the expression.
Additionally the math style of these constructs can now be detected using \cs{mathstyle}.

The old behavior can be restored by adding
\begin{verbatim}
   \mathdefaultsmode=0
\end{verbatim}
to a document.


\subsection{Fixed bug when setting hook rules for one-time hooks}

If a \cs{DeclareHookRule} command is set for a one-time hook, it has to
come \emph{before} the hook gets used, because otherwise it never
applies\Dash after all, the hook is used only once.  There was a bug in
the implementation in that the sorting mechanism was still applied if
the \cs{DeclareHookRule} declaration appeared while the one-time hook was
executed, causing the spurious typesetting of the code labels and the
hook name.  This bug is now fixed and an error is raised when a new
sorting rule is added to an already-used one-time hook.

A possible scenario in which this new error is raised is the following:
package \pkg{AAA} declares a hook rule for \hook{begindocument} (i.e.,
\cs{AtBeginDocument}) to sort out the behavior between itself and some
other package. Package \pkg{BBB} wants to load package \pkg{AAA} but
only if it hasn't been loaded in the preamble, so delays the loading to
\hook{begindocument}. In that case the hook rule declared by \pkg{AAA}
can no longer be applied and you get the error. If that happens the
solution is to load the package in \hook{begindocument/before}, which
is executed at the very end of the preamble but before
\hook{begindocument} is processed.
%
\githubissue{818}




\section{\thbox{\pkg{amsmath} 类别中宏包的修改} Changes to packages in the \pkg{amsmath} category}


\subsection{\pkg{amsopn}:\ Do not reset \cs{operator@font}}

The package \pkg{amsopn} used to define \cs{operator@font} but this
command has been provided by the \LaTeX{} format for at least 14
years. As a result the definition in \pkg{amsopn} is equivalent to a
reset to the kernel definition, which is unnecessary and surprising if
you alter the math setup (e.g., by loading a package) and at a later
stage add \pkg{amsmath}, which then undoes part of your setup. For
this reason the definition was taken out and
\pkg{amsmath}/\pkg{amsopn} now relies on the format definition.

In the unlikely event that you want the resetting to happen, use
\begin{verbatim}
  \makeatletter
   \def\operator@font{\mathgroup\symoperators}
  \makeatother
\end{verbatim}
after loading the package.
%
\githubissue{734}

\subsection{\pkg{amsmath}:\ Error in \cs{shoveleft}}

If \cs{shoveleft} started out with the words \enquote{plus} or
\enquote{minus} it was misunderstood as part of a rubber length and
led either to an error or was swallowed without trace.  By adding a
\cs{relax} this erroneous scanning into the argument of \cs{shoveleft}
is now prevented.
%
\githubissue{714}


\subsection{\pkg{amsmath} and \pkg{amsopn}:\ Robustify user commands}

Most user-level commands have been made robust in the \LaTeX{} kernel
during the last years, but variant definitions in \pkg{amsmath} turned
them back into fragile beings. We have now made most commands in
\pkg{amsmath} and \pkg{amsopn} robust as well to match the kernel
behavior. This also resolves a bug recently discovered in the
\pkg{mathtools} package, which was due to \cs{big} not being robust after
\pkg{amsmath} was loaded.
%
\githubissue{123}



\section{\pkg{graphics} 类别中宏包的修改 Changes to packages in the \pkg{graphics} category}

\subsection{公式中的颜色 Color in formulas}

While it is possible to color parts of a formula using \cs{color}
commands the approach is fairly cumbersome. For example, to color a
summation sign, but not its limits, you need four \cs{color} commands and
some seemingly unnecessary sets of braces to get coloring and spacing
right:
{\hfuzz=1pt
\begin{verbatim}
\[ X = \color{red} \sum
% without {{ the superscript below is misplaced
                    _{{\color{black} i=1}}
% without {{ the \sum is black
                    ^{{\color{black} n}}
   \color{black}    % without it the x_i is red
   x_i           \]
\end{verbatim}
}\noindent
Leaving out any of the \cs{color} commands or any of the \verb={{...}}=
will give you a wrong result instead of the desired
\[ X = \color{red} \sum
    _{{\color{black} i=1}} % without {{ the superscript is misplaced
    ^{{\color{black} n}}   % without {{ the \sum is black
   \color{black}           % without it the x_i is red
   x_i
\]
So even if this is possible, it is not a very practical solution and
furthermore there are a number of cases where it is impossible to
color a certain part of a formula, for example, an opening symbol such
as \verb=\left(= but not the corresponding \verb=\right)=.

We have therefore added the command \cs{mathcolor} to the \pkg{color}
and \pkg{xcolor} package, which has the same syntax as \cs{textcolor},
but is specially designed for use in math and handles sub and
superscripts and other aspects correctly and preserves correct
spacing. Thus, the above example can now be written as
\begin{verbatim}
\[ X = \mathcolor{red}{\sum}_{i=1}^n x_i \]
\end{verbatim}
This command is \emph{only} allowed in formulas.
For details and further examples, see \file{mathcolor.pdf}.


\subsection{Fix locating files with \cs{graphicspath}}
%

If a call to \cs{includegraphics} asked for a file (say, \file{image})
without extension, and if both \file{A/image.pdf} and \file{B/image.tex}
existed (both \file{A/} and \file{B/} in \cs{graphicspath}, but neither
in a folder searched by \TeX), then \file{A/image.pdf} would not be
found, and a \enquote{file not found} error would be incorrectly thrown.
The issue is now fixed and the graphics file is correctly found.
%
\githubissue{776}
\sxissue{q/630167}




\section{Changes to packages in the \pkg{tools} category}

\subsection{\pkg{multicol}:\ Fix \cs{newcolumn}}

The recently added \cs{newcolumn} didn't work properly if used in
vertical mode, where it behaved like \cs{columnbreak}, i.e., spreading
the column material out instead of running the column short.
%
\sxissue{q/624940}


\subsection{\pkg{bm}:\ Fix for \pkg{amsmath} operators}

An internal command used in the definition of operator commands such
as \cs{sin} in \pkg{amsmath} has been guarded in \cs{bm} to prevent
internal syntax errors due to premature expansion.
%
\githubissue{744}



\medskip

\begin{thebibliography}{9}

\fontsize{9.3}{11.3}\selectfont

\bibitem{35:blueprint} Frank Mittelbach and Chris Rowley:
  \emph{\LaTeX{} Tagged PDF \Dash A blueprint for a large project}.\\
  \url{https://latex-project.org/publications/indexbyyear/2020/}

%\bibitem{35:source2e}
%  \emph{\LaTeX{} documentation on the \LaTeX{} Project Website}.\\
%  \url{https://latex-project.org/help/documentation/}

%\bibitem{35:ltnews31} \LaTeX{} Project Team:
%  \emph{\LaTeXe{} news 31}.\\
%  \url{https://latex-project.org/news/latex2e-news/ltnews31.pdf}

\bibitem{35:ltnews32} \LaTeX{} Project Team:
  \emph{\LaTeXe{} news 32}.\\
  \url{https://latex-project.org/news/latex2e-news/ltnews32.pdf}

%\bibitem{35:ltnews33} \LaTeX{} Project Team:
%  \emph{\LaTeXe{} news 33}.\\
%  \url{https://latex-project.org/news/latex2e-news/ltnews33.pdf}

\bibitem{35:ltnews34} \LaTeX{} Project Team:
  \emph{\LaTeXe{} news 34}.\\
  \url{https://latex-project.org/news/latex2e-news/ltnews34.pdf}

\bibitem{35:ltfilehook-doc} Frank Mittelbach, Phelype Oleinik, \LaTeX{}~Project~Team:
  \emph{The \texttt{\upshape ltfilehook} documentation}.\\
  Run \texttt{texdoc} \texttt{ltfilehook-doc} to view.
\end{thebibliography}



\end{document}